---
title: "PFG-bank: Data Driven Credit Card Design"
output: html_document
---

* Team-lead gitlab id:
* Group number:
* Group name:
* Team member names:

```{r r_setup, include = FALSE}
## initial settings
knitr::opts_chunk$set(
  comment = NA,
  echo = TRUE,
  error = TRUE,
  cache = FALSE,
  message = FALSE,
  dpi = 96,
  warning = FALSE
)

## width to use when printing tables etc.
options(
  width = 250,
  scipen = 100,
  max.print = 5000,
  stringsAsFactors = FALSE
)
```

<style>
.table {
  width: auto;
}
ul, ol {
  padding-left: 18px;
}
pre, code, pre code {
  overflow: auto;
  white-space: pre;
  word-wrap: normal;
  background-color: #ffffff;
}
</style>

## Setup

Please complete this R-markdown document by answering the questions in `pfg-bank.pdf` on Dropbox (week10/readings/). The code block below will load the historical data from exhibits 1 and 2. Please DO NOT change the code used to load the data. Create an HTML (Notebook) file with all your results and comments and push both the Rmarkdown and HTML file to GitLab when you are done. All analysis results MUST be reproducible (i.e., the TA and I must be able to recreate the HTML from the R-markdown file without changes or errors).

```{r}
fp <- radiant.data::find_dropbox()
exhibit1 <- readxl::read_excel(file.path(fp, "MGTA455-2019/data/exhibits.xlsx"), sheet = "exhibit1")
exhibit2 <- readxl::read_excel(file.path(fp, "MGTA455-2019/data/exhibits.xlsx"), sheet = "exhibit2")
```

## Question answers
